---
title: "xaringan"
subtitle: "Metropolis theme"
author: "Your Name"
date: "2099/12/12"
output: 
  xaringan::moon_reader:
    css: [default, mtheme.css, fonts_mtheme.css]
    nature: 
      beforeInit: "macros.js"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

# How to use it

Specify `metropolis` and `metropolis-fonts` in the `css` argument of `moon_reader()`

```yaml
output: 
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts]
```

---
class: inverse, mline, center, middle

# Get Started

---

# Orange break lines

An orange break line is automatically added for you under the subtitle in the title slide. If you want an orange break line in a slide with class `inverse`, you need to add the class `mline` too. E.g.,

```yaml
class: inverse, mline, center, middle
```

You can also manually insert an orange break line anywhere with

```html
<hr>
```

Simply put this code directly in the `title` field of the YAML header or in the body of any slide. E.g.,

<hr>

---

# Additional tweaks

## Changing font sizes

This css comes with some classes that let you change the font-size of the coding font:
 
.code60[
```{r, eval = FALSE}
.code60[some R code with 60 % font size]
```
]
 
.code100[
```{r, eval = FALSE}
.code100[some R code with 100 % font size]
```
]

The same applies to the non-coding font by using e.g. `.font60[]`:

.font60[
xaringan is so powerful!
]

... or `.font150[]`
 
.font150[
xaringan is so powerful!
]

---

# Additional tweaks

## Inline code highlighting

I've set the look of inline code highlighting similar to the one used at `Github` with a grey background. 

---

# Differences to Metropolis Beamer
  
* No support of incremental orange break lines in break slides 

* Style of slide numbering 

---

# Header 1

## Header 2

Header 2

### Header 3

Header 3

#### Header 4

Header 4

---

class: clear

If you use `class: clear` for a slide, you can have a slide without the colored top. 
