---
title: "xaringan"
subtitle: "Metropolis theme <html><div style='float:left'></div><hr color='#EB811B' size=1px width=796px></html>"
author: "Your Name"
date: "2099/12/12"
output:
  xaringan::moon_reader:
    css: ["mtheme.css", "fonts_mtheme.css"]
    nature: 
      beforeInit: "macros.js"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

 
# How to use it

Put `mtheme.css` and `fonts_mtheme.css` in the YAML header of your xaringan presentation.     
 
``` yaml
xaringan::moon_reader:
  lib_dir: libs
  css: ["mtheme.css", "fonts_mtheme.css"]
```

You can also load it dynamically from the repository:  

``` yaml
xaringan::moon_reader:
  lib_dir: libs
  css: ["https://github.com/pat-s/xaringan-mtheme.css",
        "https://github.com/pat-s/xaringan-fonts_mtheme.css"]
```


---
class: inverse, center, middle

# Get Started

<html><div style='float:left'></div><hr color='#EB811B' size=1px width=720px></html> 

---

# Orange break lines

If you want the orange break lines in the title slide and for the slides with class `inverse`, you need to manually insert them using

```html
<html>
  <div style='float:left'></div>
  <hr color='#EB811B' size=1px width=720px>
</html> 
```

Simply put this code directly in the `title` field of the YAML header and in the body of an `inverse` slide class. 

---

# Additional tweaks

## Changing font sizes

This css comes with some classes that let you change the font-size of the coding font:
 
.code60[
```{r, eval = FALSE}
.code60[some R code with 60 % font size]
```
]
 
.code100[
```{r, eval = FALSE}
.code100[some R code with 100 % font size]
```
]

The same applies to the non-coding font by using e.g. `.font60[]`:

.font60[
xaringan is so powerful!
]

... or `.font150[]`
 
.font150[
xaringan is so powerful!
]

---

# Additional tweaks

## Inline code highlighting

I've set the look of inline code highlighting similar to the one used at `Github` with a grey background. 

---

# Differences to Metropolis Beamer
  
* No support of incremental orange break lines in break slides 

* Style of slide numbering 
